### 2024-05-05 paper/sec/6_conclusion.tex
updated

\indent Through this project, we were able to utilize computer vision 
techniques to create a program tailored to improve patient adherence to 
recovery plans in physical therapy. We consider this to be the beginning 
of a greater work with its applicability not just in physical therapy 
but also in the healthcare industry and beyond.

>>>>

\indent Through this project, we were able to successfully utilize computer vision 
techniques to create a program tailored to improve patient adherence to 
recovery plans in physical therapy. We consider this to be the beginning 
of a greater work with its applicability not just in physical therapy 
but also in the healthcare industry and beyond.
